TUDataset: A collection of benchmark datasets for learning with graphs

### 2020-05-18 main.tex
MC

@@

			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{6}{c}{\textbf{Dataset}}\\\cmidrule{3-8}
			& & {\textsc{Enyzmes}}         &  {\textsc{Imdb-Binary}}      & {\textsc{Imdb-Multi}}           & {\textsc{NCI1}}       & {\textsc{Proteins}}           & {\textsc{Reddit-Binary}}     \\	\toprule
			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &    \scriptsize $\pm  \pm  $       & \scriptsize $\pm   \pm $ &  \scriptsize $\pm  \pm   $ &  \scriptsize $\pm  \pm $ &  \scriptsize $\pm  \pm   $ & \scriptsize $\pm  \pm $  \\
				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
				& \text{WLOA} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
				& \text{GR}            &     \scriptsize $\pm  \pm$       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm \pm   $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm \pm $ & \scriptsize $\pm  \pm  $   \\
				& \text{SP}            &   \scriptsize $\pm  \pm $       &  \scriptsize $\pm  \pm  $ &  \scriptsize $\pm  \pm $ &  \scriptsize $\pm \pm  $  & \scriptsize $\pm  \pm $ &  \scriptsize $\pm\pm $  \\
			\cmidrule{2-8}	
			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GINE-$\varepsilon$}   &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
		& \text{GINE-$\varepsilon$-JK} &     \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
			\bottomrule
	\end{tabular}}
\end{table*}

@@

			& \text{GR}            &   \scriptsize $\pm    \pm  $       &   \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\  
			& \text{SP}             &    \scriptsize $\pm  \pm $       &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\   
			\cmidrule{2-7}	
			\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \text{GIN-E-$\varepsilon$}         &    \scriptsize $\pm  \pm $       & \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ \\
			& \text{GraphSage}            &    \scriptsize $\pm \pm$       & \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm $  \\
			\bottomrule
	\end{tabular}}
\end{table*}

>>>>

\cm{Add IPC paper}

@@

			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{6}{c}{\textbf{Dataset}}\\\cmidrule{3-8}
			& & {\textsc{Enyzmes}}         &  {\textsc{Imdb-Binary}}      & {\textsc{Imdb-Multi}}           & {\textsc{NCI1}}       & {\textsc{Proteins}}           & {\textsc{Reddit-Binary}}     \\	\toprule
			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &    \scriptsize $\pm  \pm  $       & \scriptsize $\pm   \pm $ &  \scriptsize $\pm  \pm   $ &  \scriptsize $\pm  \pm $ &  \scriptsize $\pm  \pm   $ & \scriptsize $\pm  \pm $  \\
%				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
%				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
				& \text{WLOA} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
				& \text{GR}            &     \scriptsize $\pm  \pm$       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm \pm   $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm \pm $ & \scriptsize $\pm  \pm  $   \\
				& \text{SP}            &   \scriptsize $\pm  \pm $       &  \scriptsize $\pm  \pm  $ &  \scriptsize $\pm  \pm $ &  \scriptsize $\pm \pm  $  & \scriptsize $\pm  \pm $ &  \scriptsize $\pm\pm $  \\
			\cmidrule{2-8}	
			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GIN-$\varepsilon$}   &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
		& \text{GIN-$\varepsilon$-JK} &     \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
			\bottomrule
	\end{tabular}}
\end{table*}

@@

			& \text{GR}            &   \scriptsize $\pm    \pm  $       &   \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\  
			& \text{SP}             &    \scriptsize $\pm  \pm $       &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\   
			\cmidrule{2-7}	
			\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \text{GINE-$\varepsilon$}         &    \scriptsize $\pm  \pm $       & \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ \\
			& \text{GINE-$\varepsilon$-JK}            &    \scriptsize $\pm \pm$       & \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm $  \\
			\bottomrule
	\end{tabular}}
\end{table*}
